---
title: 
graphics: yes
output: 
  pdf_document: 
    latex_engine: xelatex
mainfont: Calibri Light
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{grffile}
  - \usepackage{lmodern}
  - \usepackage{afterpage}
  - \usepackage{anyfontsize}
  - \usepackage{sectsty}
  - \usepackage{graphicx}
---

\definecolor{light-gray}{gray}{0.75}
\definecolor{myblue}{HTML}{002D72}
\definecolor{myred}{HTML}{D22630}
\definecolor{mygray}{HTML}{75787B}
\subsectionfont{\centering\color{myblue} \fontsize{20}{15}\selectfont}
\sectionfont{\centering \color{myred} \fontsize{40}{30}\selectfont}  

\centering
\fontsize{1.25cm}{1.25cm}\textcolor{myred}{\textbf{Community Risk Reduction Analysis}}
\vspace{40mm}

\includegraphics{C:/Logo.PNG}

\vspace{20mm}

\huge{`r FD_NAME`}

\vspace{5mm}

\normalsize
Provided by the Tennessee State Fire Marshal's Office, `r 
format(Sys.Date(),"%m/%d/%Y")`

\raggedright

\afterpage{\null\newpage}

\clearpage

\tableofcontents

\clearpage

# Community Profile

## Fire Risk in Your Response Area:

```{r setup, include=FALSE}

library(kableExtra)


```

```{r callvolume, include = TRUE}

kable(cv_t1, "latex", booktabs = T) %>%
kable_styling(position = "center")%>%
  row_spec(seq(1,nrow(cv_t1),2), background = 'light-gray')%>%
  row_spec(0, bold = TRUE)%>%
  add_header_above(c('Call Volume'=6), bold = TRUE)

kable(cv_t2, "latex", booktabs = T) %>%
kable_styling(position = "center")%>%
  row_spec(seq(1,nrow(cv_t2),2), background = 'mygray')%>%
  row_spec(0, bold = TRUE)%>%
  add_header_above(c('Fire Call Volume'=6), bold = TRUE)
  

```

